---
title       : Central Limit Theorem
subtitle    : Dynamic illustration with Rshiny App
author      : Chunxiang Zheng
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Central Limit Theorem
A statistical theory that states that given a sufficiently large sample size from a population with a finite level of variance, the mean of all samples from the same population will be approximately equal to the mean of the population.

---

## Large number of trials lead to smoother distribution

```{r echo=FALSE}
par(mfrow=c(1, 2))
dist <- replicate(100,{data <- rnorm(10)
                 mean(data)}
            )
hist(dist, main="100 repeats")

dist <- replicate(1000,{data <- rnorm(10)
                 mean(data)}
            )
hist(dist, main="1000 repeats")
```

---

## Take an average of bigger number of samples makes distribution narrower
```{r echo=FALSE}
par(mfrow=c(1, 2))
dist <- replicate(500,{data <- rnorm(10)
                 mean(data)}
            )
hist(dist, main="Average 10 numbers")
dist <- replicate(500,{data <- rnorm(100)
                 mean(data)}
            )
hist(dist, main="Average 100 numbers")
```

---

## Sample distribution other than normal distribution has same result

```{r echo=FALSE}
par(mfrow=c(1, 2))
dist <- replicate(500,{data <- rnorm(20)
                 mean(data)}
            )
hist(dist, main="Normal distribution")
dist <- replicate(500,{data <- rnorm(20)
                 mean(data)}
            )
hist(dist, main="Uniform distribution")
```



